### 2014-03-14 src/analysis.Rnw
update

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
% \begin{figure*}[t]
% <<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
% \end{figure*}
% 
% \begin{figure*}[t]
% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
% \end{figure*}
%

>>>>

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$sampling <- with(df,
      ifelse(grepl('op',strategy), 'operator(x)',
          ifelse(grepl('onelement',strategy), 'one(x)',
            ifelse(grepl('locelement',strategy), 'lines(x)',
              ifelse(grepl('withinelement',strategy), 'one(x)',
                ifelse(grepl('xceilperunit',strategy), 'ceil(x)',
                  ifelse(grepl('xpercentperunit',strategy), 'round(x)',
                    ifelse(grepl('xprobperunit',strategy), 'sample(x)',
strategy))))))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}

\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 20)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 20 (5\%)}
\label{fig:fullimgsize2}
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 10)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 10 (10\%)}
\label{fig:fullimgsize3}
\end{figure*}

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=7, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
#with(subset(stats.df,r.square > 0.9),plot(mutant.reduction, (1-r.square)*100, pch='*', col=as.factor(strategy)))
# "kind" "operator" "s.power" "s.element" "strategy" "mutant.reduction" "sd.reduction"
#  "sample" "r.square" "score.multiplier" "p.value"

df <-  subset(df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction & mutant.reduction <= 5)
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=sampling, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only mean reduction <= 5 (20\%)}
\label{fig:fullimgsize4}
\end{figure*}

% \begin{figure*}[t]
% <<op.all.2,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
% \end{figure*}
% 
% \begin{figure*}[t]
% <<op.all.4,fig.width=10, fig.height=3, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
% @
% \caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
% \end{figure*}
%

### 2014-03-14 src/methodology.Rnw
update

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
r.det$ind <- clean(r.det$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

>>>>

\begin{figure*}
<<op,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(las=1,mfrow = c(1, 2),mar=c(2,8,1,1))
o.all <- cbind(projects = rownames(o.dist.all), stack(o.dist.all))
#o.all$ind <- clean(o.all$ind)
bcol <- '#2171B5'
#bcol <- 'darkgray'
icol <- '#9ECAE0'
#icol <- 'lightgray'
o.det <- cbind(projects = rownames(o.dist.det), stack(o.dist.det))
#o.det$ind <- clean(o.det$ind)
with(o.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F, ylim=c(0,0.6), col=icol ))
with(o.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Original', cex.axis=0.8, ylim=c(0,0.6),add=T))

r.all <- cbind(projects = rownames(r.dist.all), stack(r.dist.all))
#r.all$ind <- clean(r.all$ind)
r.det <- cbind(projects = rownames(r.dist.det), stack(r.dist.det))
#r.det$ind <- clean(r.det$ind)
with(r.all,boxplot(values~ind,horizontal=T,border=c(bcol), pch='.', axes=F,ylim=c(0,0.6),  col=icol))
with(r.det,boxplot(values~ind,horizontal=T,border=c('black'), pch='.',main='Randoop', cex.axis=0.8,ylim=c(0,0.6),add=T))
@
\caption{The relative contribution of mutation operators in terms of fraction of mutants generated and detected.
The blue shade represent detected mutants, while black represents total mutants.}
\label{fig:op}
\end{figure*}

### 2014-03-14 src/paper.Rnw
.
update
udate

\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitm}{~MATH~}
%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
%\newcommand{\piti}{~INCREMENTS~}
%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
%
\newcommand{\pitnvmc}{NMC~}
\newcommand{\pitnc}{NC~}
\newcommand{\pitrc}{RC~}
\newcommand{\pitdc}{DC~}
\newcommand{\pitrv}{RV~}
\newcommand{\pitic}{IC~}
\newcommand{\pitcc}{CC~}
\newcommand{\pitemv}{EMV~}
\newcommand{\pitvmc}{VMC~}
\newcommand{\pitm}{M~}
\newcommand{\pitcb}{CB~}
\newcommand{\piti}{I~}
\newcommand{\pitri}{RI~}
\newcommand{\pitrs}{RS~}
\newcommand{\pites}{ES~}
\newcommand{\pitin}{IN~}
% No space variants.
\newcommand{\Pitnvmc}{NMC}
\newcommand{\Pitnc}{NC}
\newcommand{\Pitrc}{RC}
\newcommand{\Pitdc}{DC}
\newcommand{\Pitrv}{RV}
\newcommand{\Pitic}{IC}
\newcommand{\Pitcc}{CC}
\newcommand{\Pitemv}{EMV}
\newcommand{\Pitvmc}{VMC}
\newcommand{\Pitm}{M}
\newcommand{\Pitcb}{CB}
\newcommand{\Piti}{I}
\newcommand{\Pitri}{RI}
\newcommand{\Pitrs}{RS}
\newcommand{\Pites}{ES}
\newcommand{\Pitin}{IN}

@@

clean <- function(x)sub('CONSTRUCTOR','CONSTR',sub('RETURN','R',sub('INCREMENTS','INC',sub('VOID','V',sub('CONDITIONAL','COND',sub('NON','N',sub('VARIABLE','VAR',sub('MEMBER','MEM',sub('DELETE_','D_',sub('REMOVE_','R_',sub('NEGATE_','N_',sub('_CALLS','',sub('EXPERIMENTAL_','E_',x)))))))))))))
#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
<<>>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

@@

o.stats.sel.op <- o.stats.sel.op[,c(0,6,1,2,3,4,5)]
r.stats.sel.op <- r.stats.sel.op[,c(0,6,1,2,3,4,5)]

@@

o.stats.sel.opsel <- o.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
r.stats.sel.opsel <- r.stats.sel.opsel[,c(0,6,1,2,3,4,5)]
# 4 done

@@

<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@

>>>>

% MAX LIMIT: 10 pages for all figurs and text + any number of references.
\newcommand*\per{\scalebox{.5}{\%}}
\newcommand\Mua{Mutation analysis~}
\newcommand\mua{mutation analysis~}
%\newcommand{\pitnvmc}{~NON\_\allowbreak{}VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitnc}{~NEGATE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrc}{~REMOVE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitdc}{~DELETE\_\allowbreak{}CONDITIONALS~}
%\newcommand{\pitrv}{~RETURN\_\allowbreak{}VALUES~}
%\newcommand{\pitic}{~INLINE\_\allowbreak{}CONSTANTS~}
%\newcommand{\pitcc}{~CONSTRUCTOR\_\allowbreak{}CALLS~}
%\newcommand{\pitemv}{~E\_\allowbreak{}MEMBER\_\allowbreak{}VARIABLE~}
%\newcommand{\pitvmc}{~VOID\_\allowbreak{}METHOD\_\allowbreak{}CALLS~}
%\newcommand{\pitm}{~MATH~}
%\newcommand{\pitcb}{~CONDITIONALS\_\allowbreak{}BOUNDARY~}
%\newcommand{\piti}{~INCREMENTS~}
%\newcommand{\pitri}{~REMOVE\_\allowbreak{}INCREMENTS~}
%\newcommand{\pitrs}{~RM\_\allowbreak{}SWITCH~}
%\newcommand{\pites}{~E\_\allowbreak{}SWITCH~}
%\newcommand{\pitin}{~INVERT\_\allowbreak{}NEGATIVES~}
%
\newcommand{\pitnvmc}{NMC~}
\newcommand{\pitnc}{NC~}
\newcommand{\pitrc}{RC~}
\newcommand{\pitdc}{DC~}
\newcommand{\pitrv}{RV~}
\newcommand{\pitic}{IC~}
\newcommand{\pitcc}{CC~}
\newcommand{\pitemv}{EMV~}
\newcommand{\pitvmc}{VMC~}
\newcommand{\pitm}{M~}
\newcommand{\pitcb}{CB~}
\newcommand{\piti}{I~}
\newcommand{\pitri}{RI~}
\newcommand{\pitrs}{RS~}
\newcommand{\pites}{ES~}
\newcommand{\pitin}{IN~}
% No space variants.
\newcommand{\Pitnvmc}{NMC}
\newcommand{\Pitnc}{NC}
\newcommand{\Pitrc}{RC}
\newcommand{\Pitdc}{DC}
\newcommand{\Pitrv}{RV}
\newcommand{\Pitic}{IC}
\newcommand{\Pitcc}{CC}
\newcommand{\Pitemv}{EMV}
\newcommand{\Pitvmc}{VMC}
\newcommand{\Pitm}{M}
\newcommand{\Pitcb}{CB}
\newcommand{\Piti}{I}
\newcommand{\Pitri}{RI}
\newcommand{\Pitrs}{RS}
\newcommand{\Pites}{ES}
\newcommand{\Pitin}{IN}

@@

#options(warn=-1)
options(digits=3)
opts_chunk$set(fig.path='figure/twocolumn-', fig.align='center', fig.show='hold', echo=FALSE)
opts_chunk$set(cache=TRUE)
render_listings()
logit<-function(x) log(x/(1-x))
require(reshape2)
require(xtable)
require(ggplot2)
require(Mutsel)
@
<<chunk-hook, echo=2>>=
<<setup>>
v=data(package='Mutsel')
data(list = v$results[,3])
original.stats.df <- stats.df # save it
o.f <- function(x) subset(x, kind == 'original')
r.f <- function(x) subset(x, kind == 'randoop')
o.stats.df <- o.f(stats.df)
r.stats.df <- r.f(stats.df)
@
\end{comment}
<<>>=
theme_set(theme_bw(12))
myopts <- theme(panel.background = element_blank())

@@

@@

# 4 done

@@

<<analysis, child='analysis.Rnw'>>=
@
<<results, child='results.Rnw'>>=
@
<<results, child='discussion.Rnw'>>=
@
<<threats, child='threats.Rnw'>>=
@
<<conclusion, child='conclusion.Rnw'>>=
@
\FloatBarrier
